Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-01 doc/JFLA2022/paper.tex
Typo.

\subsection{Vision}
The \emph{Hydra-battles} project, part of \emph{Coq-community}~\cite{CoqCommunity} aims to be an experimental platform for the collaborative development of commented libraries of formal proofs. \emph{Coq-community} is a community organization that we have founded in 2018 with two goals in mind: providing a solution for the long-term maintenance of interesting Coq packages, and working collaboratively on documentation projects. The \emph{Hydra-battles} project demonstrates that these two goals are not independent: interesting Coq packages can become the basis for new documentation.
%
This umbrella project now includes evolved versions of the former Cantor and Additions libraries (under the new names of Hydra-battles and Addition-chains), the Ackerman sub-library, extracted from Russel O'Connor's Goedel library~\cite{OConnor05, Goedel} and a bridge to the Gaia library (by José Grimm~\cite{Gaia,grimm:hal-00911710}).
%
By following this approach of commenting interesting Coq packages, we provide new documentation content, that contributes to the diversity of the thriving Coq documentation ecosystem.

>>>>

\subsection{Vision}
The \emph{Hydra-battles} project, part of \emph{Coq-community}~\cite{CoqCommunity} aims to be an experimental platform for the collaborative development of commented libraries of formal proofs. \emph{Coq-community} is a community organization that we have founded in 2018 with two goals in mind: providing a solution for the long-term maintenance of interesting Coq packages, and working collaboratively on documentation projects. The \emph{Hydra-battles} project demonstrates that these two goals are not independent: interesting Coq packages can become the basis for new documentation.
%
This umbrella project now includes evolved versions of the former Cantor and Additions libraries (under the new names of Hydra-battles and Addition-chains), the Ackermann sub-library, extracted from Russel O'Connor's Goedel library~\cite{OConnor05, Goedel} and a bridge to the Gaia library (by José Grimm~\cite{Gaia,grimm:hal-00911710}).
%
By following this approach of commenting interesting Coq packages, we provide new documentation content, that contributes to the diversity of the thriving Coq documentation ecosystem.
